Democracy, Public Support, and Measurement Uncertainty

### 2021-06-02 paper/dcpo_demsupport.Rmd
change path in moc

saveRDS(result_clsUncertain_whole, file ="output/clsAJPS_uncertainty.RDS")

@@

```{r MocdcpoUncertaintyAJPS}
load("data/dcpo_ajps.rda")

@@

saveRDS(result_dcpoUncertain_whole, file ="output/dcpoAJPS_uncertainty.RDS")

@@

result_pooled <- bind_rows(
  mutate(result_clsAJPS[["pooled"]][[1]][,1:3], model = "Claassen 2020a"),
  mutate(MOCsumm(result_clsUncertain_whole[["pooled"]]), model = "Claassen w/uncertainty"),
  mutate(MOCsumm(result_dcpoUncertain_whole[[1]]), model = "DCPO")
) %>% 
  mutate(type = "Pooled")

@@

###########Regime
result_regime <- bind_rows(
  mutate(result_clsAJPS[["pooled-regime"]][[1]][,1:3], model = "Claassen 2020a"),
  mutate(MOCsumm(result_clsUncertain_whole[["pooled-regime"]]), model = "Claassen w/uncertainty"),
  mutate(MOCsumm(result_dcpoUncertain_whole[[2]]), model = "DCPO")
) %>% 
  mutate(type = "Pooled")

@@

saveRDS(result_clsUncertain, file = "ouput/clsAPSR_uncertainty.RDS")

@@

```{r  dcpoMocUncertaintyAPSR}
load("dcpo_apsr.rda")
df_dcpoUncertainAPSR <- purrr::map(1:900, function(anEntry) {
  dcpo_apsr[[anEntry]] %>% 
    plm::pdata.frame(index = c("country", "year"))
})

@@

saveRDS(result_dcpoUncertain, file ="output/dcpoAPSR_uncertainty.RDS")

>>>>

saveRDS(result_clsUncertain_whole, file =here("output","clsAJPS_uncertainty.RDS"))

@@

```{r MocdcpoUncertaintyAJPS}
load(here("data","dcpo_ajps.rda"))

@@

saveRDS(result_dcpoUncertain_whole, file =here("output","dcpoAJPS_uncertainty.RDS"))

@@

result_pooled <- bind_rows(
  mutate(result_clsAJPS[["pooled"]][[1]][,1:3], model = "Claassen 2020a"),
  mutate(MOCsumm(result_clsUncertain_whole[["pooled"]]), model = "Claassen w/uncertainty"),
  mutate(MOCsumm(result_dcpoUncertain_whole[["pooled"]]), model = "DCPO")
) %>% 
  mutate(type = "Pooled")

@@

###########Regime
result_regime <- bind_rows(
  mutate(result_clsAJPS[["pooled-regime"]][[1]][,1:3], model = "Claassen 2020a"),
  mutate(MOCsumm(result_clsUncertain_whole[["pooled-regime"]]), model = "Claassen w/uncertainty"),
  mutate(MOCsumm(result_dcpoUncertain_whole[["pooled-regime"]]), model = "DCPO")
) %>% 
  mutate(type = "Pooled")

@@

saveRDS(result_clsUncertain, file = here("ouput","clsAPSR_uncertainty.RDS"))

@@

```{r  dcpoMocUncertaintyAPSR}
load(here("data","dcpo_apsr.rda"))
df_dcpoUncertainAPSR <- purrr::map(1:900, function(anEntry) {
  dcpo_apsr[[anEntry]] %>% 
    plm::pdata.frame(index = c("country", "year"))
})

@@

saveRDS(result_dcpoUncertain, file =here("output","dcpoAPSR_uncertainty.RDS"))
